The Next Release Problem in Real World

### 2018-12-18 PaperBody.tex
Real Final~!!

In the results of the experiment.
EX1. was profit comparison. Exept for dataset with priority, the ILP has the highest result. And deterministic algorithms that AHP and ILP are very fast than heuristic algorithms. And Ex1 can answer RQ3 and RQ4. Ex2. is a comparison of the results of the profit according to the cost limit. As we mentioned, we found that limits of the Cost and the Profit had a linear relationship, regardless of algorithm. but it doesn't seem have much meaning. In RQ6. The result of algorithms were similar to those actual selection. These results show that there are no major problems with applying NRP argorithms to our dataset. Therefore, the dataset was well set to solve the NRP.

>>>>

In the results of the experiment.
EX1. was profit comparison. Except for dataset with priority, the ILP has the highest result. And deterministic algorithms that AHP and ILP are very fast than heuristic algorithms. And Ex1 can answer RQ3 and RQ4. Ex2. is a comparison of the results of the profit according to the cost limit. As we mentioned, we found that limits of the Cost and the Profit had a linear relationship, regardless of algorithm. but it doesn't seem have much meaning. In RQ6. The result of algorithms were similar to those actual selection except FIREFOX-II. These results show that there are no major problems with applying NRP algorithms to our dataset. Therefore, the dataset was well set to solve the NRP.
